Thermodynamic fragments in magic state theories

### 2020-10-20 magic_paper.tex
Added Lemma (page 11) on necessary lorenz curves comparisons"

The Lorenz curve $\lc{\noisysn}{\frac{1}{d}\id}$ consists of $n+1$ line segments, connecting at $n$ points, called \emph{elbows}, between the endpoints $(0,0)$ and $(1,1)$, as illustrated in~\cref{fig:lcsu_elbows}. 
\begin{figure}[b]
    \centering
    \includegraphics[scale=0.5]{figs/lccalcdiagram.pdf}
    \caption{\textbf{Anatomy of Strange state Lorenz curve}
    There are $n$ ``elbows'' in this Lorenz curve of an $n$-copy Strange state.
    Labels $k, k'$ indicate two elbows for the $n=4$ case.
    Their coordinates are given in~\cref{eq:lcsu_elbows}.
    }
    \label{fig:lcsu_elbows}
\end{figure}
We denote the Lorenz curve maximum as the $k_\star$-th point.
It occurs at 
\begin{align}\label{eq:lcsu_max}
	x_{k_\star} &= \frac{1}{2}\left(1 + \left( \frac{7}{9} \right)^n \right), \\
	L_{k_\star} &\equiv \lc{\noisysn}{\frac{1}{d}\id}(x_{k_\star}) = \frac{1}{2}\left (1 + \left(\frac{15-8\epsilon}{9}\right)^n \right),
\end{align}
with $k_\star = n/2$.
The coordinates of the standard Lorenz curve for a gien number of copies $n$ and noise level $\epsilon$ can be directly expressed in terms of $\Phi_+, \Phi_-$, for all $m$, $n$ the number of copies and some fixed $p \equiv p(\epsilon)$.

@@

We are now in a position to express Lorenz curve coordinates in terms of phi distributions,
\begin{equation}
	x_k(n, \epsilon) = 
	\begin{cases}
		\Phi_+(k;n,p_x),\\
		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ even}, \\
		x_{k_\star} + \Phi_-(k;n,1-p_x),\\
		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ odd}, \\
	\end{cases}	
\end{equation}
and
\begin{equation}
	L_k(n, \epsilon) = 
	\begin{cases}
		\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+(k;n,p_L),\\
		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ even}, \\
		L_{k_\star} + \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-(k;n,1-p_L),\\
		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ odd}. \\
	\end{cases}	
\end{equation}

@@

We can therefore use~\cref{lem:bounds_loose,lem:bounds_strict} to bound the standard Lorenz curves.
\begin{figure}[b]
    \centering
    \includegraphics[scale=0.5]{figs/lc_bounds.pdf}
    \caption{\textbf{Lorenz curves and bounding curves.} 
    The figure explores the distillation process of a 10-copy $0.25$-noisy Strange state to a 4-copy $0.05$-noisy Strange state in the unital fragment.
    Clearly, by looking at the Lorenz curves, the distillation process is possible.
    However the bounding curves, derived in~\cref{lem:bounds_strict}, intersect at the end, suggesting that the process is not necessarily possible.
    }
    \label{fig:lc_bounds}
\end{figure}

>>>>

The Lorenz curve $\lc{\noisysn}{\frac{1}{d}\id}$ consists of $n+1$ line segments, connecting at $n$ points, called \emph{elbows}, between the endpoints $(0,0)$ and $(1,1)$, as illustrated in~\cref{fig:lcsu_elbows}. 
\begin{figure}[b]
    \centering
    \includegraphics[scale=0.5]{figs/lccalcdiagram.pdf}
    \caption{\textbf{Anatomy of Strange state Lorenz curve}
    There are $n$ ``elbows'' in this Lorenz curve of an $n$-copy Strange state.
    Labels $k, k'$ indicate two elbows for the $n=4$ case.
    Their coordinates are given in~\cref{eq:lcsu_elbows}.
    }
    \label{fig:lcsu_elbows}
\end{figure}
We denote the Lorenz curve maximum as the $k_\star$-th point.
It occurs at 
\begin{align}\label{eq:lcsu_max}
	x_{k_\star} &= \frac{1}{2}\left(1 + \left( \frac{7}{9} \right)^n \right), \\
	L_{k_\star} &\equiv \lc{\noisysn}{\frac{1}{d}\id}(x_{k_\star}) = \frac{1}{2}\left (1 + \left(\frac{5}{3}-\frac{8}{9}\epsilon\right)^n \right),
\end{align}
with $k_\star = n/2$.
The coordinates of the standard Lorenz curve for a gien number of copies $n$ and noise level $\epsilon$ can be directly expressed in terms of $\Phi_+, \Phi_-$, for all $m$, $n$ the number of copies and some fixed $p \equiv p(\epsilon)$.

@@

We are now in a position to express Lorenz curve coordinates in terms of phi distributions,
\begin{equation}
	x_k(n, \epsilon) = 
	\begin{cases}
		\Phi_+(k;n,p_x),\\
		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ even}, \\
		x_{k_\star} + \Phi_-(k;n,1-p_x),\\
		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ odd}, \\
	\end{cases}	
\end{equation}
and
\begin{equation}
	L_k(n, \epsilon) = 
	\begin{cases}
		\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n \Phi_+(k;n,p_L),\\
		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ even}, \\
		L_{k_\star} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^n\Phi_-(k;n,1-p_L),\\
		\hspace{20pt} k\in[0,n]\ \text{and }k\text{ odd}. \\
	\end{cases}	
\end{equation}

@@

We can therefore use~\cref{lem:bounds_loose,lem:bounds_strict} to bound the standard Lorenz curves.
\begin{figure}[b]
    \centering
    \includegraphics[scale=0.4]{figs/lc_bounds.pdf}
    \caption{\textbf{Lorenz curves and bounding curves.} 
    The figure explores the distillation process of a 10-copy $0.25$-noisy Strange state to a 4-copy $0.05$-noisy Strange state in the unital fragment.
    Clearly, by looking at the Lorenz curves, the distillation process is possible.
    However the bounding curves, derived in~\cref{lem:bounds_strict}, intersect at the end, suggesting that the process is not necessarily possible.
    }
    \label{fig:lc_bounds}
\end{figure}

\subsubsection{Lorenz curve comparison}
According to~\cref{thm:dmajor}, a necessary condition for $\rho \xrightarrow{\E \in \O_\sigma} \tau$ is that $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$.
We can reduce this condition to a finite set of inequalities, defined at the elbows of $\lc{\tau}{\sigma}(x)$.
\begin{theorem}\label{thm:elbows}
	Let $\rho, \tau$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in the $\sigma$-fragment.
	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff the elbows of $\lc{\tau}{\sigma}(x)$ lie vertically below $\lc{\rho}{\sigma}(x)$.
\end{theorem}
\begin{proof}
	Let $n$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $T \coloneqq \{x_0, x_1, \dots, x_n, x_{n+1} \}$ be the set of the elbows' $x$-coordinates including $x_0 = 0$ and $x_{n+1} = 1$.

	$\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ implies $\lc{\rho}{\sigma}(x_k) \geq \lc{\tau}{\sigma}(x_k)$ for all $x_k \in T$ trivially.

	Conversely, assume that $\lc{\rho}{\sigma}(x_k) \geq \lc{\tau}{\sigma}(x_k)$ for all $x_k \in T$.
	Pick two consecutive $x$-coordinates $x_i, x_{i+1}$ and consider the line segment $\ell_\tau(x)$ connecting points $(x_i, \lc{\tau}{\sigma}(x_i))$ and $(x_{i+1}, \lc{\tau}{\sigma}(x_{i+1}))$ as well as the line segment $\ell_\rho(x)$ connecting points $(x_i, \lc{\rho}{\sigma}(x_i))$ and $(x_{i+1}, \lc{\rho}{\sigma}(x_{i+1}))$.
	This is illustrated in~\cref{fig:elbows_proof}.
\begin{figure}[h]
    \centering
    \includegraphics[scale=0.6]{figs/elbows_proof.pdf}
    \caption{\textbf{Illustration of~\cref{thm:elbows}}.
    }
    \label{fig:elbows_proof}
\end{figure}

	Due to concavity of $\lc{\rho}{\sigma}$, it is clear that for all $x \in [x_i, x_{i+1}]$, we have $\lc{\rho}{\sigma}(x) \geq \ell_\rho(x) \geq \ell_\tau(x) = \lc{\tau}{\sigma}(x)$.
	This argument can be made in all intervals $[x_i, x_{i+1}]$ with $i=0,\dots,n$, so the proof is complete.
\end{proof}

Consider now the magic state conversion,
\begin{equation}\label{eq:su_conversion}
	\noisysn \xrightarrow{\E \in \O_{\id/d}} \rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}.
\end{equation}
The Lorenz curve comparison of these states gives rise to $k$ independent necessary constraints
\begin{align}
\lc{\noisysn}{\frac{1}{d}\id}(x_1) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_1), \nonumber\\
\lc{\noisysn}{\frac{1}{d}\id}(x_2) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_2), \nonumber\\
&\vdotswithin{=} \nonumber\\
\lc{\noisysn}{\frac{1}{d}\id}(x_k) &\geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}(x_k), \nonumber
\end{align}
where $x_1, x_2, \dots, x_k$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon_{\tau})^{\otimes k}}{\frac{1}{d}\id}$.
